% Statera quick look report tables. 
\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage{longtable}

% increase table vertical line spacing:
\def\arraystretch{1.5}%

% begin doc:
\begin{document}

% price action:
\begin{longtable}[c]{ l l }
\caption{Statera high level price information. Data visually extracted from CoinGecko 2022-02-18:19:22:00 UTC.} \\
\hline
\textbf{Parameter} & \textbf{Description} \\
\hline
Token & Statera \\
Public appearance & May 24, 2020 \\
Market cap & \$7.07 million \\
Market cap rank & 1312 \\
Current price & \$0.089 \\
All time high & \$0.466 \\
All time low & \$0.00000154 \\
\hline
\end{longtable}

% tokenomics:
\begin{longtable}[c]{ l l }
\caption{Statera tokenomics at-a-glance. Data visually extracted from stateratoken.com 2022-02-18:19:22:00 UTC.} \\
\hline
\textbf{Paramter} & \textbf{Description} \\
\hline
Initial token supply & 101 million \\
Current token supply & 79.19 million \\
Available networks & Ethereum; Fantom \\
Burn mechanisms & Contract burns 1 percent of every transaction. \\
Token mints & No future mints described in official documentation. \\
Token distribution & Unknown \\
\hline
\end{longtable}

% social media
\begin{longtable}[c]{ p{0.1\textwidth} p{0.15\textwidth} p{0.1\textwidth} p{0.35\textwidth} }
\caption{Statera social media presence as of 2022-02-17.} \\
\hline
\textbf{Platform} & \textbf{Account} & \textbf{Followers} & \textbf{Notes} \\
\hline
Telegram & stateratoken & 2,194 & Quick lookover shows activity. Beware! Plenty of scam Telegram accounts with similar names though. \\
Twitter & @StateraProject & 8,863 & \\
Medium & Statera Project & 206 & Does not appear active. Last posted Nov. 14, 2021. \\
GitHub & StateraProject & 5 & Little to no activity. No public code contributions in 2022, two public contributions in 2021, and 17 contributions in 2020. \\
YouTube & Statera Project & 31 & Only one video -- "Introducing the Statera Project" -- published Sept. 24, 2021. \\
\hline
\end{longtable}

% end doc:
\end{document}
